NumPy---Array Computation for Python

### 2019-12-10 paper.tex
Add abstract

\begin{abstract}
  NumPy is the fundamental array computing library for Python.
\end{abstract}

@@

\section*{Acknowledgements}

>>>>

\begin{abstract}
  NumPy is the fundamental array computing library for Python.
  It has been actively developed for over two decades and has
  more than 850 contributors, nearly 300,000 dependent repositories
  on GitHub, and millions of downloads per year.
  It is extensively used in research and teaching.
  According to a 2018 survey, NumPy is the second most commonly used machine
  learning tool among enterprises \cite{451report2018}.
  In this article, we provide an overview of the capabilities and development
  practices of the NumPy library and highlight some recent technical
  developments.
\end{abstract}

@@

\section*{Acknowledgments}
